### 2017-05-05 paper/sections/Formalization.tex
TODO.
fix
formalization text

\begin{figure*}[htbp]
\begin{displaymath}
\begin{array}{l}
\begin{array}{llrl}
\text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I}{x}{J}{e} \\
\text{Expressions}  & e  & \Coloneqq & x \mid
e.m(\overline{e}) \mid
\new{I} \mid
e.I::m(\overline{e}) \mid
\kwsuper.I::m(e) \; \red{\mid} \; \red{v^*} \\
\text{Context}      & \Gamma & \Coloneqq & x_1:I_1 ... x_n:I_n \\
\text{\red{Values}}       & v & \Coloneqq & <I>\new{J} \\
\\
\text{Interface names} & I, J, K & & \\
\text{Method names} & m & & \\
\text{Variable names} & x & &
\end{array}
\end{array}
\end{displaymath}
\caption{Syntax. \red{*: only intended for semantic rules.}}\label{fig:syntax}
\end{figure*}

\subsection{Subtyping}
See Figure~\ref{fig:subtyping}. \haoyuan{TODO}

@@

\subsection{Typing Rules}
See Figure~\ref{fig:typingrules}. \haoyuan{TODO}

@@

\subsection{Small-step Semantics}
See Figure~\ref{fig:smallstep}. \haoyuan{TODO}

@@

\subsection{Congruence}
See Figure~\ref{fig:congruence}. \haoyuan{TODO}

@@

\haoyuan{TODO}

@@

\haoyuan{TODO. mtype(m, I) from mbody(I, I).}

@@

~\haoyuan{Unfortunately I think this example shows that it is hard to reuse
	$D.m$ on path $B$ and $E.m$ on path $B$ in $F$?}

\haoyuan{We can use the $\kwsuper$ keyword to access the originally defined methods
	in super types, but we cannot access the old updating methods.}

\haoyuan{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
a degree of freedom to $\kwsuper$, for example, $\kwsuper.D::B::m()$ is equivalent to
$\new D.B::m()$, so we can use $\kwsuper.D::B::m()$ and $\kwsuper.E::B::m()$ inside interface $F$ for code reuse?}

@@

>>>>

\begin{figure*}[htbp]
\begin{displaymath}
\begin{array}{l}
\begin{array}{llrl}
\text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e} \\
\text{Expressions}  & e  & \Coloneqq & x \mid
e.m(\overline{e}) \mid
\new{I} \mid
e.I::m(\overline{e}) \mid
\kwsuper.I::m(e) \; \red{\mid} \; \red{v^*} \\
\text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
\text{\red{Values}}       & v & \Coloneqq & <I>\new{J} \\
\\
\text{Interface names} & I, J, K & & \\
\text{Method names} & m & & \\
\text{Variable names} & x & &
\end{array}
\end{array}
\end{displaymath}
\caption{Syntax. \red{*: only intended for semantic rules.}}\label{fig:syntax}
\end{figure*}

\subsection{Subtyping and Typing Rules}
See Figure~\ref{fig:subtyping}. 
The subtyping of MIM consists of only a few rules shown in Figure ?.
In short, subtyping relations are built from the inheritance in interface
declarations. They hold both reflexivity and transitivity.

Details of type-checking rules are displayed in Figure ?, including expression
typing, well-formedness of methods and interfaces. As a convention, an environment
$\Gamma$ is maintained to store the types of variables, together with ``this'' type, namely
the enclosing type. The three rules for method invocation, (T-INVK), (T-PATHINVK) and (T-SUPERINVK)
are very similar, in the sense that they all check the type of the specific method, by using
an auxiliary function \mtype. \mtype is the function for looking up method types, which we will
illustrate later. After the method type is obtained, they all check that arguments and the receiver
have compatible types. Additionally, (T-PATHINVK) requires the receiver to be the subtype of the specified
path type, and (T-SUPERINVK) checks if the enclosing type directly extends the specified super type.

The method typing rule (T-METHOD) is more interesting, since the method update is taken into consideration.
Besides that the static type of the return expression should be the subtype of the declared return type,
we use another helper function \mostSpecific to ensure that the method update is legal. Briefly, $\mostSpecific(m, I, J)$
returns a set of interfaces, and an interface is included if and only if: (1) it originally defines method $m$; (2) it is
a supertype of $I$; (3) it is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
(4) it does not have a subtype in the same set, namely we filter out all super types.
Hence by $\mostSpecific(m, I, J) = \{J\}$ we define the legality of method updating: the updated method must be an original method (not another method update), and method updating cannot cross over method overriding.

Finally, (T-INTF) defines interface type-checking in a straightforward way.

@@

@@

\subsection{Small-step Semantics and Congruence}
Figure ? and Figure ? define small-step semantic rules and congruence rules,
respectively. When evaluating an expression, they are invoked recursively and
alternately to produce a single value in the end. The small-step semantics (S-INVK), (S-PATHINVK) and (S-SUPERINVK) behave similarly, each corresponds to
one kind of method invocation. They all invoke \mbody for method body lookup. Generally, one can understand $\mbody(m, I, J)$ in a way that it finds the most specific body of method $m$, when the receiver has dynamic type $I$ and static type $J$.
The three rules require that the receiver and the arguments have been evaluated into values, before substitution is applied.

@@

@@

@@

\red{TODO. mtype(m, I) from mbody(I, I).}

@@

~\red{Unfortunately I think this example shows that it is hard to reuse
	$D.m$ on path $B$ and $E.m$ on path $B$ in $F$?}

\red{We can use the $\kwsuper$ keyword to access the originally defined methods
	in super types, but we cannot access the old updating methods.}

\red{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
a degree of freedom to $\kwsuper$, for example, $\kwsuper.D::B::m()$ is equivalent to
$\new D.B::m()$, so we can use $\kwsuper.D::B::m()$ and $\kwsuper.E::B::m()$ inside interface $F$ for code reuse?}

@@

\red{TODO: class encapsulation problem: interface A: m; interface B: m update A; interface C: m update B.}
